Verifying Demonstrations

### 2020-07-06 paper/intro.tex

Our work present contributions in the area of \ac{DB} public-key protocols, 
particularly \ac{DB} \acp{ZKPK}.
This allows anyone to act as a verifier, unlike in the shared-key scenario 
where the verifier must be trusted.
The \ac{ZK} property also enables a variety of privacy properties, such as 
anonymity.
With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is close to a specific car, has a valid driver's license, is older than 18 
(without revealing her actual age), has the relevant car-sharing subscription which is not 
\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
and  Bob can be sure that Alice is not just relaying messages 
from her older sister Carol or \ac{DBMF} relaying the subscription from some 
unsuspecting stranger also waiting in the parking lot.

@@

We make three contributions.
First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the \ac{DFKOmodel}.
This version is based on the assumption that we can transmit all bits at once, 
not bit-by-bit as normally required for \ac{DB}.
This assumption is motivated by the results of \textcite{UWBPR}.

@@

The first (and second) contribution enables us to do distance-bounding 
privacy-preserving attribute-based credentials based on discrete logarithms, 
\eg \cite{Camenisch-phdthesis} and \cite{CLsignatures}.
We can do this by simply replacing their use of the Schnorr 
protocol~\cite{Schnorr} for \acp{ZKPK} with our protocol in this paper.
To our knowledge, no other distance-bounding protocol achieves this.
The third contribution (bit-by-bit version) also enables us to do the same, 
just without (full) \ac{DBTF} resistance.

@@

The paper is organized as follows.
\Cref{related-work} discusses some related work.
\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
send all bits at the same time.
\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
version of the protocol in practice.
\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
\Cref{formal-verification} describes our effort to formally verify the protocol 
using Tamarin.
Finally, we conclude with discussion and conclusions in 
\cref{Discussion,Conclusion}.

>>>>

Our work presents contributions in the area of \ac{DB} public-key protocols, 
particularly \ac{DB} \acp{ZKPK}.
This allows anyone to act as a verifier, unlike in the shared-key scenario 
where the verifier must be trusted.
The \ac{ZK} property also enables a variety of privacy properties, such as 
anonymity.
With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is close to a specific car, has a valid driver's license, is older than 18 
(without revealing her actual age), has the relevant car-sharing subscription which is not 
\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass}, 
and  Bob can be sure that Alice is not just relaying messages 
from her older sister Carol or \ac{DBMF} relaying the subscription from some 
unsuspecting stranger also waiting in the parking lot.

@@

We make three contributions.
First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the \ac{DFKOmodel}.
This version is based on the assumption that we can transmit all bits at once, 
not bit-by-bit as normally done for \ac{DB}.
This assumption is motivated by the results of \textcite{UWBPR}.

@@

The first (and second) contribution enables us to do distance-bounding 
privacy-preserving attribute-based credentials based on discrete logarithms, 
\eg \cite{Camenisch-phdthesis} and \cite{CLsignatures}.
We can do this by simply replacing their use of the Schnorr 
protocol~\cite{Schnorr} for \acp{ZKPK} with our protocol in this paper.
To our knowledge, no other distance-bounding protocol achieves this.
The third contribution (bit-by-bit version) also enables us to do the same, 
just without (full) \ac{DBTF} resistance. %How does the tamarin
                                %contrib come in?

@@

The paper is organized as follows.
%\Cref{related-work} discusses some related work.
\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
send all bits at the same time.
\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
version of the protocol in practice.
\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
%\Cref{formal-verification} describes our effort to formally verify the protocol 
%using Tamarin.
%Finally, we conclude with discussion and conclusions
%in \cref{Discussion,Conclusion}.
\cref{Conclusion} concludes the paper.
